---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Project 1. Insurance-Analysis

<!-- badges: start -->
<!-- badges: end -->

## Summary
Claims data were obtained from an insurer in Monterrey. According to the
data obtained it is possible to combine the risks of the insurer's portfolio. This report is
created as a support for the Risk Committee to know the structure of the risks as well as
as the influence of the claims with the variables that are known.

## Goals
1. Descriptive analysis of the variables.
2. Create categories based on the number of claims, severity, risk, etc.
3. The total value of payments is a fundamental variable for which the Committee is interested
in knowing if this is a consequence of the number of complaints and the number of
portfolio years
4. The Committee wants to find the reasons why the payment increases or decreases.Therefore, it is necessary to check if this is a consequence of variables such as location,distance etc.
5. The Committee wants to decide if special fees should be charged depending on factors
such as location, insured amount, kilometers, bonuses, etc.

## Database

```{r, echo=FALSE}
insur<-read.table("insurance.csv",header=T,sep=",")
head(insur)

```
