---
output: md_document
always_allow_html: yes

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", fig.path = "README_figs/README-"
)
```

# Project 1. Insurance-Analysis

<!-- badges: start -->
<!-- badges: end -->

## Summary
Claims data were obtained from an insurer in Monterrey. According to the
data obtained it is possible to combine the risks of the insurer's portfolio. This report is
created as a support for the Risk Committee to know the structure of the risks as well as
as the influence of the claims with the variables that are known.

## Goals
1. Descriptive analysis of the variables.
2. Create categories based on the number of claims, severity, risk, etc.
3. The total value of payments is a fundamental variable for which the Committee is interested
in knowing if this is a consequence of the number of complaints and the number of
portfolio years
4. The Committee wants to find the reasons why the payment increases or decreases.Therefore, it is necessary to check if this is a consequence of variables such as location,distance etc.
5. The Committee wants to decide if special fees should be charged depending on factors
such as location, insured amount, kilometers, bonuses, etc.

## Database

```{r, echo=FALSE}
insur<-read.table("insurance.csv",header=T,sep=",")
head(insur)

```
## 1.-Obtain a visualization that explains with an image the distribution of each of the variables.

a)Kilometres


```{r,echo=FALSE,fig=TRUE,warning=FALSE,message=FALSE }

library(dplyr)
library(plotly)
library(ggplot2)



k<-plot_ly(x=insur$Kilometres, type="histogram")%>%
 layout(title="Histogram of Kilometers",xaxis=list(title="Kilometres")
        ,yaxis=list(title="Observations"),bargap=0.1 )
k
```

b)Zones

```{r, echo=FALSE}

z<-plot_ly(x=insur$Zone, type="histogram")%>%
    layout(title="Histogram of Zones", xaxis=list(title="Zones"), yaxis=list(title="Observations"),bargap=0.1)

z
```


c)Bonus



```{r, echo=FALSE}

b<-plot_ly(x=insur$Bonus, type="histogram")%>%
 layout(title="Histogram of Bonus", xaxis=list(title="Bonus"), yaxis=list(title="Observations"),bargap=0.1)

b
```


d)Models



```{r, echo=FALSE}

m<-plot_ly(x=insur$Make, type="histogram")%>%
  layout(title="Histogram of Model", xaxis=list(title="Model"), yaxis=list(title="Observations"),bargap=0.1)

m
```


e)Insured



```{r, echo=FALSE}

i<-plot_ly(x=insur$Insured, type="histogram")%>%
 layout(title="Histogram of Insured", xaxis=list(title="Insured"), yaxis=list(title="Observations"),bargap=0.1)

i
```


f)Claims



```{r, echo=FALSE}

f<-plot_ly(x=insur$Claims, type="histogram")%>%
 layout(title="Histograma de Reclamos", xaxis=list(title="Reclamos"), yaxis=list(title="Observaciones"),bargap=0.1)

f
```


g)Payments


```{r, echo=FALSE}

g<-plot_ly(x=insur$Payment, type="histogram")%>%
  layout(title="Histogram of Payments", xaxis=list(title="Payments"), yaxis=list(title="Observations"),bargap=0.1)

g
```
## 2.-Create categories based on the number of claims, severity, risk etc.

a) Kilometres

```{r, echo=FALSE}
insurance_data_kilometres<-insur %>% group_by(Kilometres)

insurance_data_kilometres<-insur %>% group_by(Kilometres) %>% 
  summarise(sum_insured=sum(Insured), sum_claims=sum(Claims),
            sum_payments=sum(Payment))

insurance_data_kilometres<-data.frame(insurance_data_kilometres) 


plot_ly(insurance_data_kilometres, x=~Kilometres, y=~sum_insured, type='bar', name='Sum Insured per Kilometers')

plot_ly(insurance_data_kilometres, x=~Kilometres, y=~sum_claims, type='bar', name='Sum Insured per Kilometers')

plot_ly(insurance_data_kilometres, x=~Kilometres, y=~sum_payments, type='bar', name='Sum Insured per Kilometers')

```
b) Zones

```{r, echo=FALSE}

insurance_data_zones<-insur %>% group_by(Zone) %>% 
   summarise(sum_insured=sum(Insured), sum_claims=sum(Claims),
            sum_payments=sum(Payment))

insurance_data_zones<-data.frame(insurance_data_zones)

plot_ly(insurance_data_zones, x=~Zone, y=~sum_insured, type='bar', name='Sum Insured per Zones')

plot_ly(insurance_data_zones, x=~Zone, y=~sum_claims, type='bar', name='Sum Insured per Zones')

plot_ly(insurance_data_zones, x=~Zone, y=~sum_payments, type='bar', name='Sum Insured per Zones')

```

c) Model

```{r, echo=FALSE}

insurance_data_models<-insur %>% group_by(Make) %>% 
   summarise(sum_insured=sum(Insured), sum_claims=sum(Claims),
            sum_payments=sum(Payment))

insurance_data_models<-data.frame(insurance_data_models)

plot_ly(insurance_data_models, x=~Make, y=~sum_insured, type='bar', name='Sum Insured per Zones')

plot_ly(insurance_data_models, x=~Make, y=~sum_claims, type='bar', name='Sum Insured per Zones')

plot_ly(insurance_data_models, x=~Make, y=~sum_payments, type='bar', name='Sum Insured per Zones')

```


## 3.-The total value of payments is a fundamental variable for which the Committee is interested in knowing
## if this is a consequence of the number of claims and the number of years in the portfolio.


a) corr graph all variables


```{r,echo=FALSE,fig=TRUE,warning=FALSE,message=FALSE}
library(corrplot)
M<-cor(insur)
head(round(M,2))
corrplot(M, method="number")

```

b) Scatterplot - Claims

```{r,echo=FALSE,fig=TRUE,warning=FALSE,message=FALSE}

plot_ly(data = insur, x = ~Claims, y = ~Payment)

```

c) Scatterplot  - Insured

```{r,echo=FALSE,fig=TRUE,warning=FALSE,message=FALSE}

plot_ly(data = insur, x = ~Insured, y = ~Payment)

```


##4.-The Committee wants to find the variables that cause the payment to increase or decrease.
##Therefore it is necessary to check if this is a consequence of variables such as location, distance, etc.

It is necessary to perform a regression to find which variables are the most relevant (p test).

```{r, echo=FALSE}

lineModel <- lm(Payment ~ ., data = insur)
summary(lineModel) 

```

 View payments and payment averages by:
a) Insured
b) Claims
c) Kilometres


```{r, echo=FALSE}

lineModel <- lm(Payment ~ Claims, data = insur)
summary(lineModel)

insur %>% 
  plot_ly(x = ~Claims) %>% 
  add_markers(y = ~Payment) %>% 
  add_lines(x = ~Claims, y = fitted(lineModel))

```

```{r, echo=FALSE}

lineModel <- lm(Payment ~ Insured, data = insur)
summary(lineModel) 

insur %>% 
  plot_ly(x = ~Insured) %>% 
  add_markers(y = ~Payment) %>% 
  add_lines(x = ~Insured, y = fitted(lineModel))

```


```{r, echo=FALSE}

lineModel <- lm(Payment ~ Claims, data = insur)
summary(lineModel) 



insur %>% 
  plot_ly(x = ~Claims) %>% 
  add_markers(y = ~Payment) %>% 
  add_lines(x = ~Claims, y = fitted(lineModel))

```

## 5.-Finally the Committee wants to decide if fees should be charged
## depending on factors such as location, amount insured,
## miles, bonuses etc. so we need to know the cost of insure a certain risk per year.

## For that they must calculate sum(payments)/sum(insured)=cost of the risk. for each of the
## following categories:


a)Special Pay Zone


```{r, echo=FALSE}

special_pay_zone<-insur %>% group_by(Zone) %>% 
  summarise(special_pay=sum(Payment)/sum(Insured))

plot_ly(special_pay_zone, x=~Zone, y=~special_pay, type='bar', name='special_pay_zone')%>%
    layout(title="Special Pay Zone")

```

b)Special Pay Kilometres

```{r, echo=FALSE}
special_pay_kilometres<-insur %>% group_by(Kilometres) %>% 
  summarise(special_pay=sum(Payment)/sum(Insured))

plot_ly(special_pay_kilometres, x=~Kilometres, y=~special_pay, type='bar', name='special_pay_kilometres')%>%
    layout(title="Special Pay Kilometres")
```

c)Special Pay Bonus


```{r, echo=FALSE}

special_pay_bonus<-insur %>% group_by(Bonus) %>% 
  summarise(special_pay=sum(Payment)/sum(Insured))

plot_ly(special_pay_bonus, x=~Bonus, y=~special_pay, type='bar', name='special_pay_bonus')%>%
    layout(title="Special Pay Bonus")
    
 
```
